---
title: "Pengguin Palmer Analytics"
author: "Rahel"
date: "2025-11-03"
output: html_document
---

###  Setting up my environment
Notes : setting up my R environment by loading the 'tidyverse' and 'palmerpenguins' packages


```{r loading packages, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(palmerpenguins)
```
Corelation between Average body mass and flipper length among penguins in Palmer Island

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data=penguins)+
  geom_smooth(mapping=aes(x=flipper_length_mm, y=body_mass_g))+
  geom_point(mapping=aes(x=flipper_length_mm, y=body_mass_g))
```

Visualize the difference corelation body mass and flipper length across different three different species, chinstrap, gentoo, and adelie.
```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data=penguins)+
  geom_point(mapping=aes(x=flipper_length_mm, y=body_mass_g, color=species,shape=species))
```

Showing penguin distribution on different sex clustering 
```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data=penguins,aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(aes(color=species,
                 shape=species)) +
  facet_wrap(~sex)
```









 






